\documentclass[margin,line]{res}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{color}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in} 
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}
\color{black}

\name{Sara Sample, MA \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
121 North LaSalle Street  	& {Phone:}    (312) 555-1212 \\            
Suite 107			              & {E-mail:}   email@example.com \\         
Chicago, IL 60602 \\       
\end{tabular}


\section{\sc Summary}
Skilled professional seeking challenging and meaningful employment.

\section{\sc Experience}
{\bf Excelsior Services} 	\hfill {\bf Chicago, Illinois}\\
\vspace{-.3cm}
{Systems Manager} \hfill {July, 2011 - Present}\\
\vspace*{-.0in}
\begin{list2}
\item Increased system productivity by 42 percent. 
\item Managed servers and workstations for 800 employees.
\item Reduced cost of data storage.
\item Created detailed test scripts to ensure that system updates would not 
adversely impact system interface files.
\end{list2}

{\bf Coffee Slingers Datacenter} 	\hfill {\bf Elk Grove Village, Illinois}\\
\vspace{-.3cm}
{Implementation Consultant}       \hfill {September, 2007 - March, 2011}\\
\vspace*{-.0in}
\begin{list2}
\item Responsible for complete start-to-finish implementation of software, 
  managing between 5 and 11 clients at a time.
\item Created and maintained project plans, schedules, and other key documents 
  to keep the project on track for successful execution and on-time delivery.
\item Maintained integrity of client data through process of data collection, 
  conversion, and integration with other systems.
\item Collaborated with other implementation specialists to ensure an 
  integrated client implementation experience.
\item Coached clients on system usage best-practices, and assisted with 
  creation of ad-hoc and standard reports.
\end{list2}

{\bf Foundation of Starlight} (formerly Moonligt, LLC) \hfill {\bf Evanston, 
  Illinois}\\
\vspace{-.3cm}
{System Analyst} \hfill {December, 2005 - August, 2007}\\
\vspace*{-.0in}
\begin{list2}
\item Created monthly system metrics, providing senior executives 
  with a comprehensive view of key system measures.
\item Implemented complete set of QA test to allow for regular 
  system integrity checks.
\item Created and maintained database applications, allowing managers to record 
  and report on survey data.
\end{list2}

\newpage
{\bf ACME Systems} (National Headquarters) \hfill {\bf Chicago, Illinois}\\
\vspace{-.3cm}
{QA Analyst} \hfill {June, 2000 - December, 2005}\\ 
\vspace*{-.0in}
\begin{list2}
\item Automated tests, looking for problems.
\item Identified problems and documented them.
\item Accurately completed mass updates of salary information and other employment
  information into HR database.
\item Maintained employee personnel files and responded to various employee 
  requests in a professional and timely manner.
\end{list2}

\section{\sc Education}
{\bf University of Chicago}, Chicago, Illinois \\ 
\vspace{-.3cm}
\begin{list1}
\item[] Graduate Coursework in Computation Studies, 1997 - 1999
\item[] Cumulative GPA: 3.62 / 4.0
\end{list1}

\vspace*{.05in}
{\bf Harvard University}, Cambridge, Massachusetts \\
\vspace{-.3cm}
\begin{list1}
\item[] Bachelor of Science, 1997
\item[] Major: Computer Science Minor: Psychology
\end{list1}

\section{\sc Computer Skills} 
\begin{list2}
\item Primary Systems: Skilled functional user of Technical System, Program, and 
New Software. Solid knowledge of database design principles.
\item Applications: Fluent user of the MS Office suite, including Excel, Access, 
Outlook, Power Point, Word, and Visio.  
\item[] Excel: Comfortable with vlookups, pivot tables, charts, and 
formula-based data scrubbing.
\item[] Access: Comfortable with creating and modifying tables, advanced 
queries, and macros.
\item Operating Systems:  Windows, Mac OS and GNU/Linux.
\item Languages: Working knowledge of SQL, XML, XSLT, HTML, and \LaTeX.
\end{list2}

\section{\sc Activities and Honors} 
\begin{list2}
\item Active contributor to the local food bank.
\item Sponsored by Tux Systems to represent the Tux Systems documentation team 
at the annual team meeting (May, 2011) 
\item Four-year member of the University Speech Team (1993 -1997) \\
     Member of the National Championship Speech team \\
     Two-time national finalist in Humorous Speaking (1995, 1997) \\
     National quarter finalist in Informative and Persuasive Speaking (1995, 1997) \\
\end{list2}
\vspace*{-.3cm}
\centering{References available upon request.}

\end{resume}
\end{document}




